Optimal (Multiway) Spatial Joins

### 2024-06-01 msj.tex
yufei

>>>>

Let $L$ be the list of $(h, \lambda)$ pairs produced (the size of $L$ is $\out$). We now proceed to sort $L$ in ascending order of the $\lambda$-field (which is a rectangle ID). Because the IDs are integers created by the algorithm, we are permitted to sort $L$ using {\em counting sort} without violating the requirements of the comparison-based class (see Appendix~\ref{app:comp-class}). The counting sort finishes in $O(|R| + |L|) = O(n + \out)$ time, recalling that all the IDs are in $[|R|]$.
